```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(quantmod)
library(tidyquant)
library(dygraphs)
library(knitr)
library(ggplot2)
library(corrplot)
library(fPortfolio)
library(PortfolioAnalytics)
library(xts) # deal with time series data
library(ROI) # optimizer
library(ROI.plugin.glpk)
library(plotly)
library(ggpubr)
library(data.table)
library(tidyr)
library(ggcorrplot)
library(XML)
library(kableExtra)
```

```{r import data, echo=FALSE}
data.return <- read_excel("ETFfxReturns.xlsx", sheet = "Returns")
static <- read_excel("ETFfxReturns.xlsx", sheet = "Static")

colnames(data.return) <-c("time", "mkt", "rf", "AGG", "SCHP", "VCSH", "BNDX", "VWOB", "1306", "VOO", "VO", "VSS", "VGK", "VWO", "1343", "VNQ", "VNQI", "IAU", "BCI") 
Exchange <- read_excel("ETFfxReturns.xlsx", sheet = "FX")
hedge_cost <- Exchange[, c("x", "FXHCUJ12 Index", "USDJPY.Curncy")]

# data.frame(hedge_cost$"x", data.return$time)
foreignEtfs = dplyr::filter(static, static$CCY != 'JPY')$ETF

data.return[data.return==0] <- NA

##unhedged 
usdJpy = Exchange$USDJPY.Curncy + 1
for (etf in foreignEtfs) {
  data.return[etf] <- (1 + data.return[etf]) * (usdJpy) - 1
}

#remove all the 0 returns as these are the times affected by public holidays
data.return <- na.omit(data.return)

```

```{r processing data (annualization & currency), echo=FALSE}
# All etf returns are available from 2001-10-01 to 2022-03-18

# Convert data.return to xts object
Alldata_xts <- xts(data.return[,2:19], order.by = as.Date(data.return$time))
rownames(Alldata_xts) <- as.Date(Alldata_xts$time)

# Covert daily return for etfs to xts object (remove mkt and rf)
etf_returns_xts <- xts(data.return[,4:19], order.by = as.Date(data.return$time))
rownames(etf_returns_xts) <-as.Date(etf_returns_xts$time)

# Covert mkt return to xts object
mkt_xts <- xts(data.return[,2], order.by = as.Date(data.return$time))
rownames(mkt_xts) <-as.Date(mkt_xts$time)

# Covert rf return to xts object
rf_xts <- xts(data.return[,3], order.by = as.Date(data.return$time))
rownames(rf_xts) <-as.Date(rf_xts$time)

hedge_xts <- xts(hedge_cost, order.by = as.Date(hedge_cost$x))
rownames(hedge_xts) <-as.Date(hedge_cost$x)

annual_fn <- function(daily_return) {
  return (prod(1 + daily_return, na.rm=TRUE) - 1)
  }

#252 trading days
# Weekly return
weekly_return_xts <- NULL
for (i in 4:19){
  temp <- xts(data.return[,i], order.by = as.Date(data.return$time))
  temp <- apply.weekly(temp,annual_fn)
  weekly_return_xts <- cbind(weekly_return_xts, temp)
}

# Monthly return
monthly_return_xts <- NULL
for (i in 4:19){
  temp <- xts(data.return[,i], order.by = as.Date(data.return$time))
  temp <- apply.monthly(temp,annual_fn)
  monthly_return_xts <- cbind(monthly_return_xts, temp)
}

# Annual return
Yearly_return_xts <- NULL
for (i in 4:19){
  temp <- xts(data.return[,i], order.by = as.Date(data.return$time))
  temp <- apply.yearly(temp,annual_fn)
  Yearly_return_xts <- cbind(Yearly_return_xts, temp)
}

# Annual market rate
annual_mkt_xts <- apply.yearly(mkt_xts,  FUN = annual_fn)
# monthly market rate
monthly_mkt_xts <- apply.monthly(mkt_xts,  FUN = annual_fn)

# Annual risk free rate
annual_rf_xts <- apply.yearly(rf_xts, FUN = annual_fn)
# monthly risk free rate
monthly_rf_xts <- apply.monthly(rf_xts,  FUN = annual_fn)

##getting rid of VO and VGK
daily_clean <- etf_returns_xts[, -c(8, 10)]
Yearly_clean <- Yearly_return_xts[, -c(8, 10)]
monthly_clean <- monthly_return_xts[, -c(8, 10)]
```

\pagebreak

```{r CAPM, include=FALSE}
#CAPM Regression
rk.free <-mean(monthly_mkt_xts)
mkt.mu <- mean(monthly_rf_xts)

coef_ETFs <- NULL
for (i in 1:14){
  beta <- lm((monthly_clean[,i] - monthly_rf_xts) ~ (monthly_mkt_xts-monthly_rf_xts))
  coef_ETFs <- data.frame(cbind(coef_ETFs, beta$coefficients))
}

colnames(coef_ETFs) <- colnames(monthly_clean)
rownames(coef_ETFs) <- c("alpha", "beta")
kable(coef_ETFs)
miu <- mean(monthly_clean)
sd <- sd(monthly_clean)

historical_data <- rbind(miu, sd)
kable(historical_data)

capm.mu <- rk.free + coef_ETFs[2,]*(mkt.mu - rk.free) 
kable(capm.mu)

```

\pagebreak

\renewcommand{\arraystretch}{1.5}
```{r ETF Information Table, fig.width=5, echo=FALSE, include=TRUE}
ETF_Names = c("AGG", "SCHP", "VCSH", "BNDX", "VWOB", 
              "1306.T", "VOO", "VSS", "VWO", 
              "1343.T", "VNQ", "VNQI", 
              "IAU", "BCI")

# find corresponding information in Yahoo finance
summaryTable = NA
for (code in ETF_Names) {
    dataURL <- paste('https://finance.yahoo.com/quote/', code, '?p=', code, sep="")
    webpage <- readLines(dataURL, warn= FALSE)
    html <- htmlTreeParse(webpage, useInternalNodes = TRUE, asText = TRUE)
    tableNodes <- getNodeSet(html, "//table")
    current_ETF_Info <- readHTMLTable(tableNodes[[2]])
    summaryTable <- rbind(summaryTable, current_ETF_Info$V2)
    colnames(summaryTable) <- current_ETF_Info$V1
}

# remove NA row + add in ETF names
summaryTable <- summaryTable[-1,]
rownames(summaryTable) <- ETF_Names
summaryTable <- as.data.frame(summaryTable)

# drop useless categories
removedCategories <- c("NAV", "PE Ratio (TTM)", "Beta (5Y Monthly)", "YTD Daily Total Return")
summaryTable <- summaryTable[, !(names(summaryTable) %in% removedCategories)]

ETF_Currencies <- c("USD", "USD", "USD", "USD","USD", 
                    "JPY", "USD", "USD", "USD", 
                    "JPY", "USD", "USD", 
                    "USD", "USD")

Asset_Types <- c("US Intemediate Bond", "US TIPS ETF", "US Short Term Bond", "International Bond Index Fund", "Government Bond", 
                 "Exchange Traded Fund", "S&P500",  "All-World ex-US Small-Cap Index", "Emerging Markets Index Fund",
                 "JP REIT", "Real Estate Index Fund ", "ex-U.S. Real Estate Index Fund", 
                 "Gold", "Commodity")

Asset_Classes <- c("USIGFI", "TIPFI", "USSTCorpFI", "GFI", "EMFI2",
                 "JEQ", "USEQ", "WexUSsEQ", "EMEQ", 
                 "JREIT", "USREIT ", "GREIT", 
                 "GOLD", "COMMO")

# calculate beta for each ETF
capm_regression <- data.frame(t(coef_ETFs[, colnames(coef_ETFs)]))

# combine the information into one table
summaryTable <- cbind(ETF_Currencies, Asset_Types, summaryTable, round(capm_regression$beta, 3))

# change column names
names(summaryTable)[1] <- paste("Currency")
names(summaryTable)[2] <- paste("Asset Type")
names(summaryTable)[7] <- paste("Beta")

# categorize into following groups
Fixed_Income_Group <- summaryTable[1:5,]
Equity_Group <- summaryTable[6:9,]
REIT_Group <- summaryTable[10:12,]
Gold_Commodity_Group <- summaryTable[13:14,]

kable(summaryTable, caption = "ETF Summary Table", align = "c") %>% 
  kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"), position = "center") %>% 
  pack_rows(index = c("Fixed Income" = 5, "Equity" = 4, "Real Estate Investment Trust" = 3, "Gold and Commodity" = 2)) %>%
  column_spec(1:8, width = "5em") %>%
  row_spec(0, bold = T)
```

```{r fixed income, echo=FALSE, include=TRUE}
kable(Fixed_Income_Group, caption = "Fixed Income", align = "c") %>% 
  kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"), position = "center") %>%
  column_spec(1:8, width = "5em")
```

```{r equity, echo=FALSE, include=TRUE}
kable(Equity_Group, caption = "Equity", align = "c") %>% 
  kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"), position = "center") %>%
  column_spec(1:8, width = "5em")
```
```{r REIT, echo=FALSE, include=TRUE}
kable(REIT_Group, caption = "Real Estate Investment Trust", align = "c") %>% 
  kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"), position = "center") %>%
  column_spec(1:8, width = "5em")
```

```{r Gold_Com, echo=FALSE, include=TRUE}
kable(Gold_Commodity_Group, caption = "Gold and Commodity", align = "c") %>% 
  kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"), position = "center") %>%
  column_spec(1:8, width = "5em")
```
\pagebreak

## Efficient Frontier  
After examination of core statistics and correlation (refer to Appendix 1) of the given ETFs, the team decided on 14 ETFs from 4 asset classes, Fixed Income (AGG, SCHP, VCSH, BNDX, VWOB), Equity (1306, VOO, VSS, VWO,), REIT (1343, VNQ, VNQI) and Commodity (IAU, BCI).
```{r efficient frontier, echo=FALSE, out.width="70%",fig.align = 'center'}
# ---- FRONTIERPLOT ----
rk.free <-  mean(monthly_rf_xts)

## generate 200 portfolio on the frontier
Spec.rf <- portfolioSpec()
setNFrontierPoints(Spec.rf) <- 1000
setRiskFreeRate(Spec.rf) <- rk.free
myret <- as.timeSeries(monthly_clean)

## constraints 
nFunds <- NCOL(monthly_clean)
REIT.group <- paste0("maxsumW[10:12]=0.1")
Comm.group <- paste0("maxsumW[13:14]=0.1")
max.const <- paste0("maxW[1:14]=0.3")
high.bound = c(REIT.group, Comm.group, max.const)

mymvf <- portfolioFrontier(myret, Spec.rf, constraints = high.bound)
plot(mymvf, c(1,2,3,4))
# tailoredFrontierPlot(mymvf,sharpeRatio = FALSE)

frontierWeights <- getWeights(mymvf)
colnames(frontierWeights) <- colnames(monthly_clean)
risk_return <- frontierPoints(mymvf)
```

```{r weighst, echo=FALSE,out.width="70%",fig.align = 'center'}
#plotting frontier weights
Spec<- portfolioSpec()
setNFrontierPoints(Spec) <- 100
setRiskFreeRate(Spec) <- rk.free
weightsPlot(portfolioFrontier(myret, Spec, constraints = high.bound))
```

\pagebreak

```{r Portfolio Build, echo=FALSE}
# select point for different  level of Risks Portfolio
l = 250
m = 300
h = 330
```

## Low Risk Portfolio
The Low Risk Portfolio consists of 71.47 % Fixed Income (30.00% SCHP, 28.90% AGG, 12.57% VWOB), 8.53% of Equity (8.53% 1306), 10% of REIT (10% 1343) and 10% of Commodities (10% IAU). The domestic ETFs are Equity 1306 and REIT 1343.
The annualized return is 3.38% and the annualized risk is 7.98%.
```{r Low Risk Portfolio, echo=FALSE, out.width="70%",fig.align = 'center'}
# Getting Low Risk Portfolio infor
mvp.weights <- frontierWeights[l,]
low.risk.weights <- mvp.weights
low.risk.mean <-getTargetReturn(mymvf)[l,]["mean"]
low.risk.risk <- getTargetRisk(mymvf)[l,]["Cov"]

# annualized return
low.risk.annual_return <-round(((1+low.risk.mean)^12-1)*100, 2) ## annualized return% return and r 
# annualized risk
low.risk.annual_risk <- round(low.risk.risk*sqrt(12)*100, 2) ## annualized risk% risk.

## ggplot MVP weights
etf <- colnames(frontierWeights)
df.mvp <- data.frame(mvp.weights)
index <- c()
for(i in 1:nrow(df.mvp)) {
  if (df.mvp[i,"mvp.weights"] != 0) {
    index <- c(index,i)
    }
}

final.etf.name <- c()
for (i in index) {
  final.etf.name <- c(final.etf.name,etf[i])
}

low.risk.etf.index <- index
low.risk.etf.name <- final.etf.name

df.mvp= df.mvp[df.mvp['mvp.weights'] != 0]
final.weights <- df.mvp
df.mvp <- data.frame(df.mvp)

low.risk.etf.weights <- final.weights

bargraph <- ggplot(data = df.mvp, aes(x = final.etf.name, y = final.weights, fill = final.etf.name)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_text(aes (label = sprintf("%.02f %%", final.weights * 100)),
              position = position_dodge(width = 0.9),size = 2.8, vjust = -0.15, check_overlap = TRUE) +
  theme(legend.position="none") + 
  ggtitle("Low Risk Portfolio Weights") + theme(plot.title = element_text(hjust = 2))   + labs(x = "ETFs", y = "Weights (%)")

## ggplot pie

piechart <- ggplot(df.mvp, aes(x = "", y = final.weights, fill = final.etf.name)) +
  geom_col() + labs(fill = "ETFs") + 
  # geom_text(size = 3,aes(label = sprintf("%.02f %%", final.weights * 100)), position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") + theme_void()

#combine two graphs
ggarrange(bargraph,piechart)

## asset class weight distribution 
FI.w <- round(sum(low.risk.weights[1:5])*100,2)
EQ.w <- round(sum(low.risk.weights[6:9])*100,2)
REIT.w <- format(round(sum(low.risk.weights[10:12])*100,2), nsmall = 2)
COMMO.w <- format(round(sum(low.risk.weights[13:14])*100,2), nsmall =2)
All.weights.low <- as.data.frame(cbind(FI.w, EQ.w, REIT.w, COMMO.w))
colnames(All.weights.low) <- c("Fixed Income", "Equity", "Real Estate", "Commodities")
rownames(All.weights.low) <- c("Percentage (%)")
kable(All.weights.low, align = "c") %>% kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"), position = "center")
```

```{r Low Risk Portfolio cum return, echo=FALSE,out.width="70%",fig.align = 'center'}
## cumulative return of Low risk portfolio

tickers = low.risk.etf.name
wts = low.risk.etf.weights
wts_tbl <- tibble(ETFS = tickers,
                  wts = wts)
ret_data <- as.data.table(monthly_clean[,low.risk.etf.index])
colnames(ret_data) <-c("date", tickers)
ret_data <- pivot_longer(ret_data, cols = c(2,3,4,5), names_to = "ETFS", values_to = "Revenue")
ret_data <- left_join(ret_data,wts_tbl, by = 'ETFS')
ret_data <- ret_data %>%
  mutate(wt_return = wts * Revenue)
 
port_ret <- ret_data %>%
  group_by(date) %>%
  summarise(port_ret = sum(wt_return))

port_cumulative_ret <- port_ret %>%
  mutate(cr = cumprod(1 + port_ret))

low_cr <- port_cumulative_ret

port_cumulative_ret %>%
  ggplot(aes(x = date, y = cr)) +
  geom_line() +
  labs(x = 'Date',
       y = 'Cumulative Returns',
       title = 'Low Risk Portfolio Cumulative Returns') +
  theme_classic() +
  scale_y_continuous(breaks = seq(1,5,0.2)) +
  scale_x_date(date_breaks = '3 years',
               date_labels = '%Y')
```

\pagebreak

## Medium Risk Portfolio
The Medium Risk Portfolio consists of 65.38 % Fixed Income (30.00% SCHP, 5.38% AGG, 30% VWOB), 14.62% of Equity ( 14.62% 1306), 10% of REIT (10% 1343) and 10% of Commodities (10% IAU). The domestic ETFs are Equity 1306 and REIT 1343.
The annualized return is 3.89% and the annualized risk is 8.90%. 
```{r Medium Risk Portfolio, echo=FALSE, out.width="70%",fig.align = 'center'}
# Getting Medium Risk Portfolio infor
mvp.weights <- frontierWeights[m,]
med.risk.weights <- mvp.weights
med.risk.mean <-getTargetReturn(mymvf)[m,]["mean"]
med.risk.risk <- getTargetRisk(mymvf)[m,]["Cov"]

# annualized return
med.risk.annual_return <-round(((1+med.risk.mean)^12-1)*100, 2) ## annualized return% return and r 
# annualized risk
med.risk.annual_risk <- round(med.risk.risk*sqrt(12)*100, 2) ## annualized risk% risk.

## ggplot MVP weights
etf <- colnames(frontierWeights)
df.mvp <- data.frame(mvp.weights)
index <- c()
for(i in 1:nrow(df.mvp)) {
  if (df.mvp[i,"mvp.weights"] != 0) {
    index <- c(index,i)
    }
}

final.etf.name <- c()
for (i in index) {
  final.etf.name <- c(final.etf.name,etf[i])
}

medium.risk.etf.index <- index
medium.risk.etf.name <- final.etf.name

df.mvp= df.mvp[df.mvp['mvp.weights'] != 0]
final.weights <- df.mvp
df.mvp <- data.frame(df.mvp)

medium.risk.etf.weights <- final.weights

bargraph <- ggplot(data = df.mvp, aes(x = final.etf.name, y = final.weights, fill = final.etf.name)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_text(aes (label = sprintf("%.02f %%", final.weights * 100)),
              position = position_dodge(width = 0.9),size = 2.8, vjust = -0.15, check_overlap = TRUE) +
  theme(legend.position="none") + 
  ggtitle("Medium Risk Portfolio Weights") + theme(plot.title = element_text(hjust = 2))   + labs(x = "ETFs", y = "Weights (%)")

## ggplot pie
piechart <- ggplot(df.mvp, aes(x = "", y = final.weights, fill = final.etf.name)) +
  geom_col() + labs(fill = "ETFs") + 
  # geom_text(size = 3,aes(label = sprintf("%.02f %%", final.weights * 100)), position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") + theme_void()

#combine two graphs
ggarrange(bargraph,piechart)

## asset class weight distribution 
FI.w <- round(sum(med.risk.weights[1:5])*100,2)
EQ.w <- round(sum(med.risk.weights[6:9])*100,2)
REIT.w <- format(round(sum(med.risk.weights[10:12])*100,2), nsmall = 2)
COMMO.w <- format(round(sum(med.risk.weights[13:14])*100,2), nsmall =2)
All.weights.med <- as.data.frame(cbind(FI.w, EQ.w, REIT.w, COMMO.w))
colnames(All.weights.med) <- c("Fixed Income", "Equity", "Real Estate", "Commodities")
rownames(All.weights.med) <- c("Percentage (%)")
kable(All.weights.med, align = "c") %>% kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"), position = "center")
```

```{r med Risk Portfolio cum return, echo=FALSE,out.width="70%",fig.align = 'center'}
## cumulative return of Medium risk portfolio

tickers = medium.risk.etf.name
wts = medium.risk.etf.weights
wts_tbl <- tibble(ETFS = tickers,
                  wts = wts)
ret_data <- as.data.table(monthly_clean[,medium.risk.etf.index])
colnames(ret_data) <-c("date", tickers)
ret_data <- pivot_longer(ret_data, cols = c(2,3,4,5), names_to = "ETFS", values_to = "Revenue")
ret_data <- left_join(ret_data,wts_tbl, by = 'ETFS')
ret_data <- ret_data %>%
  mutate(wt_return = wts * Revenue)
 
port_ret <- ret_data %>%
  group_by(date) %>%
  summarise(port_ret = sum(wt_return))

port_cumulative_ret <- port_ret %>%
  mutate(cr = cumprod(1 + port_ret))

medium_cr <- port_cumulative_ret

port_cumulative_ret %>%
  ggplot(aes(x = date, y = cr)) +
  geom_line() +
  labs(x = 'Date',
       y = 'Cumulative Returns',
       title = 'Medium Risk Portfolio Cumulative Returns') +
  theme_classic() +
  scale_y_continuous(breaks = seq(1,5,0.2)) +
  scale_x_date(date_breaks = '3 years',
               date_labels = '%Y')
```

\pagebreak

## High Risk Portfolio
The High Risk Portfolio consists of 46.28% Fixed Income (16.28% SCHP, 30% VWOB), 33.72% of Equity (3.72% VOO, 30% 1306), 10% of REIT (10% 1343) and 10% of Commodities (10% IAU). The domestic ETFs are Equity 1306 and REIT 1343.
The annualized return is 4.19% and the annualized risk is 10.22%. 
```{r High Risk Portfolio, echo=FALSE, out.width="70%",fig.align = 'center'}
# Getting High Risk Portfolio infor
mvp.weights <- frontierWeights[h,]
high.risk.weights <- mvp.weights
high.risk.mean <-getTargetReturn(mymvf)[h,]["mean"]
high.risk.risk <- getTargetRisk(mymvf)[h,]["Cov"]

# annualized return
high.risk.annual_return <-round(((1+high.risk.mean)^12-1)*100, 2) ## annualized return% return and r 
# annualized risk
high.risk.annual_risk <- round(high.risk.risk*sqrt(12)*100, 2) ## annualized risk% risk.

## ggplot MVP weights
etf <- colnames(frontierWeights)
df.mvp <- data.frame(mvp.weights)
index <- c()
for(i in 1:nrow(df.mvp)) {
  if (df.mvp[i,"mvp.weights"] != 0) {
    index <- c(index,i)
    }
}

final.etf.name <- c()
for (i in index) {
  final.etf.name <- c(final.etf.name,etf[i])
}

high.risk.etf.index <- index
high.risk.etf.name <- final.etf.name

df.mvp= df.mvp[df.mvp['mvp.weights'] != 0]
final.weights <- df.mvp
df.mvp <- data.frame(df.mvp)

high.risk.etf.weights <- final.weights

bargraph <- ggplot(data = df.mvp, aes(x = final.etf.name, y = final.weights, fill = final.etf.name)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_text(aes (label = sprintf("%.02f %%", final.weights * 100)),
              position = position_dodge(width = 0.9),size = 2.8, vjust = -0.15, check_overlap = TRUE) +
  theme(legend.position="none") + 
  ggtitle("High Risk Portfolio Weights") + theme(plot.title = element_text(hjust = 2))   + labs(x = "ETFs", y = "Weights (%)")

# ##ggplot pie
# bar.mvp <- ggplot(df.mvp, aes(x = "", y = final.weights, fill = final.etf.name)) +
#   geom_bar(stat = "identity", width = 1) +
#   ggtitle("Minimum Variance Portfolio (unhedged) Optimal Weights")
# pie <- bar.mvp + coord_polar("y", start = 0)
# pie + theme_minimal()

piechart <- ggplot(df.mvp, aes(x = "", y = final.weights, fill = final.etf.name)) +
  geom_col() + labs(fill = "ETFs") + 
  # geom_text(size = 3,aes(label = sprintf("%.02f %%", final.weights * 100)), position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") + theme_void()

#combine two graphs
ggarrange(bargraph,piechart)

## asset class weight distribution 
FI.w <- round(sum(high.risk.weights[1:5])*100,2)
EQ.w <- round(sum(high.risk.weights[6:9])*100,2)
REIT.w <- format(round(sum(high.risk.weights[10:12])*100,2), nsmall = 2)
COMMO.w <- format(round(sum(high.risk.weights[13:14])*100,2), nsmall =2)
All.weights.high <- as.data.frame(cbind(FI.w, EQ.w, REIT.w, COMMO.w))
colnames(All.weights.high) <- c("Fixed Income", "Equity", "Real Estate", "Commodities")
rownames(All.weights.high) <- c("Percentage (%)")
kable(All.weights.high, align = "c") %>% kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"), position = "center")
```

```{r high Risk Portfolio cum return, echo=FALSE, out.width="70%",fig.align = 'center'}
## cumulative return of High risk portfolio

tickers = high.risk.etf.name
wts = high.risk.etf.weights
wts_tbl <- tibble(ETFS = tickers,
                  wts = wts)
ret_data <- as.data.table(monthly_clean[,high.risk.etf.index])
colnames(ret_data) <-c("date", tickers)
ret_data <- pivot_longer(ret_data, cols = c(2,3,4,5), names_to = "ETFS", values_to = "Revenue")
ret_data <- left_join(ret_data,wts_tbl, by = 'ETFS')
ret_data <- ret_data %>%
  mutate(wt_return = wts * Revenue)
 
port_ret <- ret_data %>%
  group_by(date) %>%
  summarise(port_ret = sum(wt_return))

port_cumulative_ret <- port_ret %>%
  mutate(cr = cumprod(1 + port_ret))

high_cr <- port_cumulative_ret

port_cumulative_ret %>%
  ggplot(aes(x = date, y = cr)) +
  geom_line() +
  labs(x = 'Date',
       y = 'Cumulative Returns',
       title = 'High Risk Portfolio Cumulative Returns') +
  theme_classic() +
  scale_y_continuous(breaks = seq(1,5,0.5)) +
  scale_x_date(date_breaks = '3 years',
               date_labels = '%Y')
```
\pagebreak

## Equal Weights Portfolio
For back testing purpose, the team included the equal weight portfolio as a reference benchmark.
The High Risk Portfolio consists of 7.14% of each ETF. Fixed Income totals 35.71%, Equity totals 28.57%, REITs totals 21.43% and Commodities totals 14.29%.  
The annualized return is 2.87% and the annualized risk is 11.05%. 
```{r Equal Weights Portfolio, echo=FALSE, out.width="70%",fig.align = 'center'}
Spec.rf <- portfolioSpec()
setRiskFreeRate(Spec.rf) <- rk.free
myret <- as.timeSeries(monthly_clean)
nFunds <- ncol(monthly_clean)
setWeights(Spec.rf) <- rep(1/nFunds, times = nFunds)
#feasiblePortfolio() calculates the properties of the portfolio
ewP <- feasiblePortfolio(myret, Spec.rf)
equal.mean <- getTargetReturn(ewP)["mean"]
equal.risk <- getTargetRisk(ewP)["Cov"]
equal.risk.etf.weights <- getWeights(ewP)
# annualized return
equal.annual_return <-round(((1+equal.mean)^12-1)*100, 2) ## annualized return% return and r 

# annualized risk
equal.annual_risk <- round(equal.risk*sqrt(12)*100, 2) ## annualized risk% risk.

## asset class weight distribution 
FI.w <- round(100/14*5, 2)
EQ.w <- round(100/14*4, 2)
REIT.w <- format(round(100/14*3, 2), nsmall = 2)
COMMO.w <- format(round(100/14*2, 2), nsmall = 2)
All.weights.ewp <- as.data.frame(cbind(FI.w, EQ.w, REIT.w, COMMO.w))
colnames(All.weights.ewp) <- c("Fixed Income", "Equity", "Real Estate", "Commodities")
rownames(All.weights.ewp) <- c("Percentage (%)")
kable(All.weights.ewp, align = "c") %>% kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"), position = "center")
```

```{r equal portfolio cum return, echo=FALSE, out.width="70%",fig.align = 'center'}

tickers = colnames(monthly_clean)
wts = equal.risk.etf.weights
wts_tbl <- tibble(ETFS = tickers,
                  wts = wts)
ret_data <- as.data.table(monthly_clean)
colnames(ret_data) <-c("date", tickers)
ret_data <- pivot_longer(ret_data, cols = c(2,3,4,5), names_to = "ETFS", values_to = "Revenue")
ret_data <- left_join(ret_data,wts_tbl, by = 'ETFS')
ret_data <- ret_data %>%
  mutate(wt_return = wts * Revenue)
 
port_ret <- ret_data %>%
  group_by(date) %>%
  summarise(port_ret = sum(wt_return))

port_cumulative_ret <- port_ret %>%
  mutate(cr = cumprod(1 + port_ret))

equal_cr <- port_cumulative_ret

port_cumulative_ret %>%
  ggplot(aes(x = date, y = cr)) +
  geom_line() +
  labs(x = 'Date',
       y = 'Cumulative Returns',
       title = 'Equal Weights Portfolio Cumulative Returns') +
  theme_classic() +
  scale_y_continuous(breaks = seq(1,5,0.2)) +
  scale_x_date(date_breaks = '3 years',
               date_labels = '%Y')
```

\pagebreak
## Cumulative Returns Comparasion
From the cumulative return plots, we can see that the 3 portfolios constructed have higher returns from 2005 onwards, despite fluctuations in the Cumulative returns. From the graph, we can see that high risk portfolio has the highest yearly cumulative returns, while the equal weight portfolio has the lowest. Japanese investors could choose the portfolio within their own risk tolerance. Yet, all 3 portfolio have higher annualized return and lower annualized risks than the equal weight portfolio. 
```{r combined return, echo=FALSE, fig.width = 15, fig.height= 8, fig.align = 'center'}
## plot cumulative return for the different risk portfolio
combined_cr <- data.frame(
   date <- low_cr$date,
   low <- low_cr$cr,
   mid <- medium_cr$cr,
   high <- high_cr$cr,
   equal <- equal_cr$cr)
colnames(combined_cr) <- c("date", "low", "mid", "high", "equal")
ggplot(combined_cr, aes(date)) +
  geom_line(aes(y=low, colour="Low Risk")) +
  geom_line(aes(y=mid, colour="Mid Risk")) +
  geom_line(aes(y=high, colour="High Risk")) +
  geom_line(aes(y=equal, colour="Equal Weights")) +
  scale_color_manual(name = "Portfolio Risk Level",
  values = c( "Low Risk" = "darkolivegreen3", "Mid Risk" = "deepskyblue1", "High Risk" = "red", "Equal Weights" = "black"),
  labels = c("Low Risk", "Mid Risk", "High Risk", "Equal Weights")) +
  xlab("Date") + ylab("Cumulative Return") +
  ggtitle("Cumulative Returns Comparasion")


## table for return and risk comparison
annual.return.summary <- c(low.risk.annual_return, med.risk.annual_return, high.risk.annual_return, equal.annual_return)
annual.risk.summary <- c(low.risk.annual_risk, med.risk.annual_risk, high.risk.annual_risk, equal.annual_risk)
annual.combine <- cbind(annual.return.summary,annual.risk.summary)
colnames(annual.combine) <- c("Annualized Return %", "Annualized Risk %")
rownames(annual.combine) <- c("Low Risk", "Medium Risk", "High Risk","Equal Weights" )
kable(annual.combine, align = "c") %>% kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"), position = "center")
```

\pagebreak

## *Appendix 1:* 
## Methodology for ETFs choosing:  
Having correlated assets can increase potential risk of portfolio.  


*Removal of VO:*  
The correlation between ETFs VOO and VO is very high, with a correlation of 0.97.  
They are both foreign stocks belonging to the fund family Vanguard, but VO is more aggressive with higher risk. Also, VOO has an expense ratio of 0.03% while VO has a higher expense ratio of 0.04%. Furthermore, VOO has a higher number of holding of 506 than VO's 361. Therefore, VO will be removed from this portfolio exercise.

*Removal of VGK:*  
There is a high correlation of VGK with both VOO and VO of 0.87 and also a high correlation with VWO, which is 0.86. VGK is an European equity with diversified sector weightings. The team believes that VWO will exhibit better diversity in terms of geographic locations, as it includes emerging markets around the world and also developed markets including EU. VWO also has a similar sector weightings. Both these two ETFs have expense ratio of 0.08%, while VWO has higher market cap than VGK. Therefore, VGK is removed as comparatively, VWO allows the team to diversify the portfolio more, especially geographically.

## Correlation Coefficient Comparasion
```{r correlation, echo=FALSE, out.width="88%", fig.align = 'center'}
cor.matrix <- cor(data.return[, -c(1,2,3)])
# half portfolio
ggcorrplot(cor.matrix, hc.order = TRUE, type = "lower", lab_size = 3,
   lab = TRUE)
# # Clustered Correlation plot
# corrplot(corr = cor.matrix, method = "circle", 
#          order = "hclust", addrect = 4, rect.col = "blue",
#          tl.col = "black", tl.cex = 0.5,addCoef.col = "white",
#          number.font = 0.8, number.cex = 0.5)
```

\pagebreak

## *Appendix 2:* 
## Methodology  
1. Examination of various ETFs  
   - Currency Conversion
   - Identification of composition of the ETFs
   - Analysis of correlation of selected ETFs
   - Finalize the ETF selection for portfolio construction
   - Aim at a granular and diversified portfolio

2. Analysis of core characteristics and statistics of ETFs  
   - Initial investigations on returns: Weekly, Monthly, Annual Return
   - Asset classes and sectors identification of ETFs (Fixed income, Equity, Commodities)
  
3. Perform CAPM Regression  
   - Obtain beta, alpha, mu, sd for each ETF based on the CAPM Regression: $R^*_{i, t} = \alpha_{i} + \beta_{i}R^*_{m,t}$ 

4. Portfolio Construction
   - Set objectives for portfolio
   - Generation of Efficient Frontier
   - Modified individual and group constraints for the portfolio to ensure diversification: 10% for REITs and Commodities, 30% for individual ETFs. Constraints are imposed so that the weights of single portfolio are in a reasonable range. 
   - Generation of Global Minimum Variance Portfolio
   - Selection of Low, Medium and High risk portfolio from the efficient frontier: points on the efficient portfolio are selected to construct portfolios meeting the needs of investors' different risk tolerance. For low, medium and high risk portfolio, the weight of fixed income is set to be 70%, 60% and 50% (giving some leeway), while meeting the constraints specified above. 

5. Portfolio Performance Analysis  
   - Showcase cumulative returns for each risk level portfolio
   - Use EWP to compare with the performance of the portfolios

\pagebreak

## *Appendix 3:* 
## Global Minimum Variance Portfolio
```{r GMVP, echo=FALSE, out.width="88%",fig.align = 'center'}
# Getting Minimum Variance Portfolio
Spec.rf <- portfolioSpec()
setRiskFreeRate(Spec.rf) <- rk.free
yr <- as.timeSeries(monthly_clean)
mvp <- minvariancePortfolio(myret, Spec.rf, const = high.bound)
mvp.weights <- getWeights(mvp)

 
## ggplot MVP weights
etf <- colnames(frontierWeights)
df.mvp <- data.frame(mvp.weights)
index <- c()
for(i in 1:nrow(df.mvp)) {
  if (df.mvp[i,"mvp.weights"] != 0) {
    index <- c(index,i)
    }
}
final.etf.name <- c()
for (i in index) {
  final.etf.name <- c(final.etf.name,etf[i])
}
df.mvp= df.mvp[df.mvp['mvp.weights'] != 0]
final.weights <- df.mvp
df.mvp <- data.frame(df.mvp)


bargraph <- ggplot(data = df.mvp, aes(x = final.etf.name, y = final.weights, fill = final.etf.name)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_text(aes (label = sprintf("%.02f %%", final.weights * 100)),
              position = position_dodge(width = 0.9),size = 2.8, vjust = -0.15, check_overlap = TRUE) +
  theme(legend.position="none") + 
  ggtitle("Global Minimum Variance Portfolio (unhedged) Optimal Weights") + theme(plot.title = element_text(hjust = -.2))   + labs(x = "ETFs", y = "Weights (%)")

## ggplot pie
piechart <- ggplot(df.mvp, aes(x = "", y = final.weights, fill = final.etf.name)) +
  geom_col() + labs(fill = "ETFs") + 
  # geom_text(size = 3,aes(label = sprintf("%.02f %%", final.weights * 100)), position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") + theme_void()

#combine two graphs
ggarrange(bargraph,piechart)

## asset class weight distribution 
FI.w <- format(round(sum(mvp.weights[1:5])*100,2), nsmall = 2)
EQ.w <- format(round(sum(mvp.weights[6:9])*100,2), nsmall = 2)
REIT.w <- format(round(sum(mvp.weights[10:12])*100,2), nsmall = 2)
COMMO.w <- format(round(sum(mvp.weights[13:14])*100,2), nsmall =2)
All.weights.gmvp <- as.data.frame(cbind(FI.w, EQ.w, REIT.w, COMMO.w))
colnames(All.weights.gmvp) <- c("Fixed Income", "Equity", "Real Estate", "Commodities")
rownames(All.weights.gmvp) <- c("Percentage (%)")
kable(All.weights.gmvp, align = "c") %>% kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"), position = "center")
```